Twists of supersymmetric gauge theories

### 2019-08-26 paper.tex
merge

\tikzstyle{s16} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=red!30]
\tikzstyle{s16chiral} = [s16, dashed]
\tikzstyle{s8} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
\tikzstyle{s4} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=green!30]
\tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

We call $\cE$ the {\bf space of BV fields}.  The pairing $\omega$ equips the algebra of local functionals on $E$ with a shifted Poisson bracket, in the following way.
\begin{definition}
The \emph{BV antibracket} $\{-,-\}$ is the \chris{give at least an informal definition and a reference to a formal definition in the book \cite{Book2}.  Also cite \cite{WittenAntibracket}.}
\end{definition}

>>>>

\tikzstyle{s16} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=red!30]
\tikzstyle{s16chiral} = [s16, dashed]
\tikzstyle{s8 } = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
\tikzstyle{s4} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=green!30]
\tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

We call $\cE$ the {\em space of BV fields}.  
The pairing $\omega$ equips the algebra of local functionals on $E$ with a shifted bracket, in the following way.
In Section 3 of \cite{CosRenorm}, it is shown that to every {\em local} functional $f \in \cO(\cE)$ there exists a symplectic vector field $X_f$ on $\cE$ whose Hamiltonian function is $f$. 
Note that if $f$ is degree $n$, then $X_f$ is of degree $n+1$ due to the degree of $\omega$.

\begin{definition}
The {\bf BV antibracket} $\{-,-\}$ is the bilinear map of cohomological degree $+1$
\[
\{-,-\} : \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE)
\]
defined by sending a pair $(f,g)$ to the local functional $X_f (g)$.
\chris{Also cite \cite{WittenAntibracket}.}
\end{definition}

This pairing is graded symmetric and satisfies the graded Jacobi identity.
Note that since local functionals do not form an algebra, it is not a (shifted) Poisson bracket.
